Dags

### 2021-07-13 04_reports/dags.Rmd
its been a while (new edits to Sonja's edits)

---
title: "Dags"
output:
  xaringan::moon_reader
---

```{tikz, echo = FALSE, fig.cap = "Pin1 as biomarker and risk of dementia"}
\usetikzlibrary{arrows}
\begin{tikzpicture}[node distance=2cm]
\node (p) {$P_0$};
\node [above of = p, yshift = -1cm, xshift = 1cm](l) {$L$};
\node [right of = p, gray!30] (dp) {$D_t$};
\node [right of = dp, gray!30] (pstar) {$P^*_t$};
\node [right of = pstar, gray!30] (d) {$D_{t+1}$};
\node [right of = d] (y) {$Y_{t+1}$};
\node [below of = dp, yshift = 1cm, xshift = 1cm, gray!30](c) {$C_1$};
\node [below of = d, yshift = 1cm, xshift = 1cm, gray!30](cd) {$C_2$};
\draw[->, gray!30] (p) -- (dp);
\draw[->] (l) -- (p);
\draw[->] (l) to [out=0,in=90, looseness=0.4] (y);
\draw[->, semithick] (p) to [out=45,in=135, looseness=0.3] (y);
\draw[->, gray!30] (dp) -- (pstar);
\draw[->, gray!30] (p) to [out=45,in=135, looseness=0.3] (pstar);
\draw[->, gray!30] (pstar) -- (d);
\draw[->, gray!30] (p) to [out=45,in=135, looseness=0.3] (d);
\draw[->, gray!30] (d) -- (y);
\draw[->, gray!30] (c) -- (dp);
\draw[->, gray!30] (c) -- (pstar);
\draw[->, gray!30] (cd) -- (d);
\draw[->, gray!30] (cd) -- (y);
\end{tikzpicture}
```

@@

```{tikz, echo = FALSE, fig.cap = "Cancer diagnosis as proxy for Pin1 expression"}
\usetikzlibrary{arrows}
\begin{tikzpicture}[node distance=2cm]
\node (p) {$P_0$};
\node [above of = p, yshift = -1cm, xshift = 1cm, gray!30](l) {$L$};
\node [right of = p, gray!30] (dp) {$D_t$};
\node [right of = dp] (pstar) {$P^*_t$};
\node [right of = pstar, gray!30] (d) {$D_{t+1}$};
\node [right of = d] (y) {$Y_{t+1}$};
\node [below of = dp, yshift = 1cm, xshift = 1cm, gray!30](c) {$C_1$};
\node [below of = d, yshift = 1cm, xshift = 1cm, gray!30](cd) {$C_2$};
\draw[->, gray!30] (p) -- (dp);
\draw[->, gray!30] (l) -- (p);
\draw[->, gray!30] (l) to [out=0,in=90, looseness=0.4] (y);
\draw[->, semithick] (p) to [out=+45,in=+135, looseness=0.3] (y);
\draw[->, gray!30] (dp) -- (pstar);
\draw[->] (p) to [out=45,in=135, looseness=0.3] (pstar);
\draw[->, gray!30] (pstar) -- (d);
\draw[->, gray!30] (p) to [out=+45,in=+135, looseness=0.3] (d);
\draw[->, gray!30] (d) -- (y);
\draw[->, gray!30] (c) -- (dp);
\draw[->, gray!30] (c) -- (pstar);
\draw[->, gray!30] (cd) -- (d);
\draw[->, gray!30] (cd) -- (y);
\end{tikzpicture}
```

```{tikz, echo = FALSE, fig.cap = "Survival bias when treating cancer diagnosis as the proxy for Pin1 expression"}

\usetikzlibrary{arrows}
\begin{tikzpicture}[node distance=2cm]
\node (p) {$P_0$};
\node [above of = p, yshift = -1cm, xshift = 1cm, gray!30](l) {$L$};
\node [right of = p] (dp) {$D_t$};
\node [right of = dp] (pstar) {$P^*_t$};
\node [right of = pstar, gray!30] (d) {$D_{t+1}$};
\node [right of = d] (y) {$Y_{t+1}$};
\node [below of = dp, yshift = 1cm, xshift = 1cm](c) {$C_1$};
\node [below of = d, yshift = 1cm, xshift = 1cm, gray!30](cd) {$C_2$};
\draw[->] (p) -- (dp);
\draw[->, gray!30] (l) -- (p);
\draw[->, gray!30] (l) to [out=0,in=90, looseness=0.4] (y);
\draw[->, semithick] (p) to [out=+45,in=+135, looseness=0.3] (y);
\draw[->] (dp) -- (pstar);
\draw[->] (p) to [out=45,in=135, looseness=0.3] (pstar);
\draw[->, gray!30] (pstar) -- (d);
\draw[->, gray!30] (p) to [out=+45,in=+135, looseness=0.3] (d);
\draw[->] (d) -- (y);
\draw[->] (c) -- (dp);
\draw[->] (c) -- (pstar);
\draw[->, gray!30] (cd) -- (d);
\draw[->, gray!30] (cd) -- (y);
\end{tikzpicture}
```

```{tikz, echo = FALSE, fig.cap = "Death as a competing event for dementia over follow-up"}
\usetikzlibrary{arrows}
\begin{tikzpicture}[node distance=2cm]
\node (p) {$P_0$};
\node [above of = p, yshift = -1cm, xshift = 1cm, gray!30](l) {$L$};
\node [right of = p, gray!30, gray!30] (dp) {$D_t$};
\node [right of = dp, gray!30] (pstar) {$P^*_t$};
\node [right of = pstar] (d) {$D_{t+1}$};
\node [right of = d] (y) {$Y_{t+1}$};
\node [below of = dp, yshift = 1cm, xshift = 1cm, gray!30](c) {$C_1$};
\node [below of = d, yshift = 1cm, xshift = 1cm, gray!30](cd) {$C_2$};
\draw[->, gray!30] (p) -- (dp);
\draw[->, gray!30] (l) -- (p);
\draw[->, gray!30] (l) to [out=0,in=90, looseness=0.4] (y);
\draw[->, semithick] (p) to [out=+45,in=+135, looseness=0.3] (y);
\draw[->, gray!30] (dp) -- (pstar);
\draw[->, gray!30] (p) to [out=45,in=135, looseness=0.3] (pstar);
\draw[->, gray!30] (pstar) -- (d);
\draw[->, gray!30] (p) to [out=+45,in=+135, looseness=0.3] (d);
\draw[->] (d) -- (y);
\draw[->, gray!30] (c) -- (dp);
\draw[->, gray!30] (c) -- (pstar);
\draw[->, gray!30] (cd) -- (d);
\draw[->, gray!30] (cd) -- (y);
\end{tikzpicture}
```

```{tikz, echo = FALSE, fig.cap = "Direct effect"}
\usetikzlibrary{arrows}
\begin{tikzpicture}[node distance=2cm]
\node (p) {$P_0$};
\node [above of = p, yshift = -1cm, xshift = 1cm, gray!30](l) {$L$};
\node [right of = p, gray!30, gray!30] (dp) {$D_t$};
\node [right of = dp] (pstar) {$P^*_t$};
\node [right of = pstar] (d) {$D_{t+1}$};
\node [right of = d] (y) {$Y_{t+1}$};
\node [below of = dp, yshift = 1cm, xshift = 1cm, gray!30](c) {$C_1$};
\node [below of = d, yshift = 1cm, xshift = 1cm](cd) {$C_2$};
\draw[->, gray!30] (p) -- (dp);
\draw[->, gray!30] (l) -- (p);
\draw[->, gray!30] (l) to [out=0,in=90, looseness=0.4] (y);
\draw[->, semithick] (p) to [out=+45,in=+135, looseness=0.3] (y);
\draw[->, gray!30] (dp) -- (pstar);
\draw[->] (p) to [out=45,in=135, looseness=0.3] (pstar);
\draw[->] (pstar) -- (d);
\draw[->] (p) to [out=+45,in=+135, looseness=0.3] (d);
\draw[->] (d) -- (y);
\draw[->, gray!30] (c) -- (dp);
\draw[->, gray!30] (c) -- (pstar);
\draw[->] (cd) -- (d);
\draw[->] (cd) -- (y);
\end{tikzpicture}
```

```{tikz, echo = FALSE, fig.cap = "Direct effect"}
\usetikzlibrary{arrows}
\begin{tikzpicture}[node distance=2cm]
\node (p) {$P_0$};
\node [above of = p, yshift = -1cm, xshift = 1cm](l) {$L$};
\node [right of = p] (dp) {$D_t$};
\node [right of = dp] (pstar) {$P^*_t$};
\node [right of = pstar] (d) {$D_{t+1}$};
\node [right of = d] (y) {$Y_{t+1}$};
\node [below of = dp, yshift = 1cm, xshift = 1cm](c) {$C_1$};
\node [below of = d, yshift = 1cm, xshift = 1cm](cd) {$C_2$};
\draw[->] (p) -- (dp);
\draw[->] (l) -- (p);
\draw[->] (l) to [out=0,in=90, looseness=0.4] (y);
\draw[->, semithick] (p) to [out=+45,in=+135, looseness=0.3] (y);
\draw[->] (dp) -- (pstar);
\draw[->] (p) to [out=45,in=135, looseness=0.3] (pstar);
\draw[->] (pstar) -- (d);
\draw[->] (p) to [out=+45,in=+135, looseness=0.3] (d);
\draw[->] (d) -- (y);
\draw[->] (c) -- (dp);
\draw[->] (c) -- (pstar);
\draw[->] (cd) -- (d);
\draw[->] (cd) -- (y);
\end{tikzpicture}
```

>>>>

---
title: "Dags"
output: word_document
---
## Current DAG
```{tikz, echo = FALSE}
\usetikzlibrary{arrows}
\begin{tikzpicture}[node distance=2cm]
\node (p) {$P_{t-1}$};
\node [above of = p, yshift = -0.8cm, xshift = -1cm](l) {$L$};
\node [below of = p, yshift = 1cm] (pstar) {$P^*_{t-1}$};
\node [right of = p] (dp) {$D_t$};
\node [right of = dp] (p2) {$P_t$};
\node [below of = p2, yshift = 1cm] (pstar2) {$P^*_t$};
\node [right of = p2] (dp2) {$D_{t+1}$};
\node [right of = dp2] (y) {$Y_{t+1}$};
\node [below of = dp2, yshift = 1cm, xshift = +1cm](cd) {$C$};
\draw[->] (p) to (pstar);
\draw[->] (l) -- (p);
\draw[->] (l) to (dp);
\draw[->] (pstar) -- (dp);
\draw[->] (dp) to [out=-45,in=-135, looseness=0.3] (dp2);
\draw[->] (dp) -- (p2);
\draw[->, semithick] (p) to [out=+45,in=+135, looseness=0.3] (y);
\draw[->] (p2) to (pstar2);
\draw[->] (dp2) -- (y);
\draw[->] (cd) -- (dp2);
\draw[->] (cd) -- (y);
\draw[->] (l) -- (p2);
\draw[->] (l) to [out=0,in=90, looseness=0.4] (dp2);
\draw[->] (l) to [out=0,in=90, looseness=0.4] (y);
\draw[->] (pstar2) -- (dp2);
\draw[->, semithick] (p2) to [out=+45,in=+135, looseness=0.3] (y);
\end{tikzpicture}
```

---
## Changing time and L
```{tikz, echo = FALSE}
\usetikzlibrary{arrows}
\begin{tikzpicture}[node distance=2cm]
\node (p) {$P_t$};
\node [above of = p, yshift = -0.8cm, xshift = -1cm](l) {$L_1$};
\node [below of = p, yshift = 1cm] (pstar) {$P^*_t$};
\node [right of = p] (dp) {$D_{t+1}$};
\node [right of = dp] (p2) {$P_{t+1}$};
\node [below of = p2, yshift = 1cm] (pstar2) {$P^*_{t+1}$};
\node [right of = p2] (dp2) {$D_{t+k}$};
\node [right of = dp2] (y) {$Y_{t+k}$};
\node [below of = dp2, yshift = 1cm, xshift = +1cm](cd) {$L_2$};
\draw[->] (p) to (pstar);
\draw[->] (l) -- (p);
\draw[->] (l) to (dp);
\draw[->] (pstar) -- (dp);
\draw[->] (dp) to [out=-45,in=-135, looseness=0.3] (dp2);
\draw[->] (dp) -- (p2);
\draw[->, semithick] (p) to [out=+45,in=+135, looseness=0.3] (y);
\draw[->] (p2) to (pstar2);
\draw[->] (dp2) -- (y);
\draw[->] (cd) -- (dp2);
\draw[->] (cd) -- (y);
\draw[->] (l) -- (p2);
\draw[->] (l) to [out=0,in=90, looseness=0.4] (dp2);
\draw[->] (l) to [out=0,in=90, looseness=0.4] (y);
\draw[->] (pstar2) -- (dp2);
\draw[->, semithick] (p2) to [out=+45,in=+135, looseness=0.3] (y);
\end{tikzpicture}
```

---
## Changing time, L and proxy
```{tikz, echo = FALSE}
\usetikzlibrary{arrows}
\begin{tikzpicture}[node distance=2cm]
\node (p) {$P_t$};
\node [above of = p, yshift = -0.8cm, xshift = -1cm](l) {$L_1$};
\node [below of = p, yshift = 1cm] (pstar) {$C_t$};
\node [right of = p] (dp) {$D_{t+1}$};
\node [right of = dp] (p2) {$P_{t+1}$};
\node [below of = p2, yshift = 1cm] (pstar2) {$C_{t+1}$};
\node [right of = p2] (dp2) {$D_{t+k}$};
\node [right of = dp2] (y) {$Y_{t+k}$};
\node [below of = dp2, yshift = 1cm, xshift = +1cm](cd) {$L_2$};
\draw[->] (p) to (pstar);
\draw[->] (l) -- (p);
\draw[->] (l) to (dp);
\draw[->] (pstar) -- (dp);
\draw[->] (dp) to [out=-45,in=-135, looseness=0.3] (dp2);
\draw[->] (dp) -- (p2);
\draw[->, semithick] (p) to [out=+45,in=+135, looseness=0.3] (y);
\draw[->] (p2) to (pstar2);
\draw[->] (dp2) -- (y);
\draw[->] (cd) -- (dp2);
\draw[->] (cd) -- (y);
\draw[->] (l) -- (p2);
\draw[->] (l) to [out=0,in=90, looseness=0.4] (dp2);
\draw[->] (l) to [out=0,in=90, looseness=0.4] (y);
\draw[->] (pstar2) -- (dp2);
\draw[->, semithick] (p2) to [out=+45,in=+135, looseness=0.3] (y);
\end{tikzpicture}
```

@@

## Changing time, L and proxy, plus L to C
```{tikz, echo = FALSE}
\usetikzlibrary{arrows}
\begin{tikzpicture}[node distance=2cm]
\node (p) {$P_t$};
\node [above of = p, yshift = -0.8cm, xshift = -1cm](l) {$L_1$};
\node [below of = p, yshift = 1cm] (pstar) {$C_t$};
\node [right of = p] (dp) {$D_{t+1}$};
\node [right of = dp] (p2) {$P_{t+1}$};
\node [below of = p2, yshift = 1cm] (pstar2) {$C_{t+1}$};
\node [right of = p2] (dp2) {$D_{t+k}$};
\node [right of = dp2] (y) {$Y_{t+k}$};
\node [below of = dp2, yshift = 1cm, xshift = +1cm](cd) {$L_2$};
\draw[->] (p) to (pstar);
\draw[->] (l) -- (p);
\draw[->] (l) -- (pstar);
\draw[->] (l) to (dp);
\draw[->] (pstar) -- (dp);
\draw[->] (dp) to [out=-45,in=-135, looseness=0.3] (dp2);
\draw[->] (dp) -- (p2);
\draw[->, semithick] (p) to [out=+45,in=+135, looseness=0.3] (y);
\draw[->] (p2) to (pstar2);
\draw[->] (dp2) -- (y);
\draw[->] (cd) -- (dp2);
\draw[->] (cd) -- (y);
\draw[->] (l) -- (p2);
\draw[->] (l) to [out=-45,in=-180, looseness=0.4] (pstar2);
\draw[->] (l) to [out=0,in=90, looseness=0.4] (dp2);
\draw[->] (l) to [out=0,in=90, looseness=0.4] (y);
\draw[->] (pstar2) -- (dp2);
\draw[->, semithick] (p2) to [out=+45,in=+135, looseness=0.3] (y);
\end{tikzpicture}
```
